Use of significance test logic by scientists in a novel reasoning task

### 2020-06-04 inst/manuscript/manuscript.Rmd
minor additions for RSOS

data_accessibility: |
  All materials, code, and data are freely available at https://github.com/richarddmorey/Morey_Hoekstra_StatCognition.

@@

>>>>

data_accessibility: |
  Data and relevant code for this research work are stored in GitHub: https://github.com/richarddmorey/Morey_Hoekstra_StatCognition and have been archived within the Zenodo repository: https://doi.org/10.5281/zenodo.3877106

@@

* **Funding**: This research was not supported by external funding.
